\documentclass[letterpaper]{resume}

\usepackage{multibbl}
\usepackage{bibtopic}
\usepackage[numbers,sort&compress]{natbib}  % for bibliography
\usepackage{multicol}
\renewcommand{\bibsection}[0]{}  % removing bibliography header


\begin{document}

\author{Eric W H Hutton}
\email{eric.hutton@colorado.edu}
\phone{303.492.6233}
\webpage{csdms.colorado.edu}
\streetaddress{1560 30th St.}
\citystatezip{Boulder, CO 80309}

\maketitle


\section{Professional Preparation}

\affiliation[B.A.Sc., Engineering Physics]{University of British Columbia}{1992--1997}

\begin{compactitem}[\itembullet]
  \item Geophysics option
\end{compactitem}

\affiliation[Ph.D., Geophysics]{University of Colorado}{2002--2007}

\begin{compactitem}[\itembullet]
  \item Graduate Certificate in Oceanography
  \item Graduate Certificate in Hydrology
\end{compactitem}

\section{Appointments}

\affiliation[Research Scientist]{INSTAAR, University of Colorado
Boulder, CO}{2007--present}

\affiliation[Professional Research Assistant]{INSTAAR, University of Colorado
Boulder, CO}{1997--2007}

%\section{Publication Summary}
%\begin{compactitem}[\itembullet]
%  \item 21 peer-reviewed journal publications (additional 6 in press)
%  \item 2 peer-reviewed book chapters
%  \item 6 peer-reviewed conference proceedings
%  \item 31 published conference abstracts
%\end{compactitem}


\begin{btSect}{./huttone-five-relevant}
\section{Products}
\btPrintNotCited
\end{btSect}

\begin{btSect}{./huttone-five-other}
\section{Other Products}
\btPrintNotCited
\end{btSect}

\section{Synergistic Activities}
\renewcommand{\labelenumi}{[\arabic{enumi}]}

\subsection {Community Standards for Model Coupling}
%\begin{compactitem}
\begin{enumerate}
  \setcounter{enumi}{0}
  \item BMI: \textit {A Basic Modeling Interface Standard, Version 0.9}. The Community Surface Dynamics Modeling System,
        \url {http://csdms.colorado.edu/wiki/BMI_Description}.
  \item CSDMS Standard Names: \textit {A Model Variable Naming Standard, Version 0.9}. The Community Surface Dynamics Modeling System,
        \url {http://csdms.colorado.edu/wiki/CSDMS_Standard_Names}.
\end{enumerate}
%\end{compactitem}

\subsection {Model-Coupling Education Through Short Courses \& Conference Sessions}
\begin{enumerate}
%\begin{compactitem}[\itembullet]
  \setcounter{enumi}{2}
  \item \textit {Plug-and-play Modeling with the Web Modeling Tool}. Two-hour short-course. CSDMS Conference 2014, Boulder, Colorado, USA.
  \item \textit {Modeling coupled processes with sedflux}. Two-hour short-course. CSDMS Conference 2011, Boulder, Colorado, USA.
  \item \textit {Earth-Surface Dynamics Modeling: Model Coupling}. Two-hour short-course. RCEM Conference 2009, Santa Fe, Argentina.
%  \item Modeling and Model Coupling across the Earch Surface. Frontiers in Computational Physics: Modeling the Earth System. Boulder, Colorado. Dec. 2012.
\end{enumerate}
%\end{compactitem}

%\subsection {Session Organizer}
%\begin{compactitem}[\itembullet]
%\end{compactitem}

%\subsection {Organizations}
%\begin{compactitem}[\itembullet]
%\begin{enumerate}
%  \setcounter{enumi}{4}
%  \item The Community Surface Dynamics Modeling System
%  \begin{compactitem}[\itembullet]
%    \item Chief software engineer, 2008-present
%  \end{compactitem}
%\end{enumerate}
%\end{compactitem}

%\subsection {Lecture}
%\begin{compactitem}[\itembullet]
%  \item Producing \textsc{CSDMS}-compliant Morphodynamic Code to Share with the RCEM Community. RCEM Conference 2009, Santa Fe, Argentina.
%\end{compactitem}

%\nocite{*}
%\bibliographystyle{agufull08-rev}
%\bibliography{huttone-citations}

%\newbibliography{papers}

%\newbibliography{abstracts}
%\bibliographystyle{abstracts}{agufull08-rev}

%\nocite{papers}{*}
%\btPrintNotCited
%\bibliography{papers}{huttone-citations}{Papers}
%\bibliography{abstracts}{huttone-abstracts}{Abstracts}

\section{Collaborators \& Other Affiliations}
\subsection{Collaborators}
\begin{multicols}{2}
\begin{compactitem}[\itembullet]

  \item Achille, Gaetano, Instituto Nazionale di Astrofisca
  \item Adams, Jordan, Tulane
  \item Ashton, Andrew,  WHOI
  \item Brown, Jed, University of Colorado
  \item Esposito, Fancesca, Osservatorio Astronomico di Capodimonte
  \item Gasparini, Nicole, Tulane
  \item Giosan, Liviu, WHOI
  \item Hill, Mary, University of Kansas
  \item Hobley, Dan, University of Colorado
  \item Hoke, Hynek, University of Colorado
  \item Hynek, Brian, University of Colorado
  \item Istanbulluoglu, Erkan, University of Washington
  \item Kallumadikal, Jisamma
  \item Kettner, Albert, University of Colorado
  \item Maselli, Vittorio, ISMAR-CNR
  \item Nienhuis, Jaap, WHOI
  \item Norris, Boyana, University of Oregon
  \item Nudurupati, Sai, University of Washington
  \item Overeem, Irina, University of Colorado
  \item Piper, Mark, University of Colorado
  \item Rossi, Angelo, International Space Science Institute
  \item Trincardi, Fabio, ISMAR-CNR
  \item Tucker, Greg, University of Colorado
  \item Wallis, Jillian, University of Southern California
  \item Watts, Allan, Oxford
  \item Xing, Fei, University of Colorado
  \item Zissimopoulos, Julie, University of Southern California
\end{compactitem}
\end{multicols}

\subsection{Graduate Advisors}
\begin{multicols}{2}
\begin{compactitem}[\itembullet]
  \item Prof. R. Anderson, University of Colorado.
  \item Dr. S.D. Peckham; University of Colorado
  \item Prof. J. Pitlick, University of Colorado
  \item Prof. T. Pfeffer, University of Colorado
\end{compactitem}
\end{multicols}

\subsection{Doctoral Advisor}
\begin{compactitem}[\itembullet]
  \item Prof. J.P.M. Syvistski; Director of CSDMS at INSTAAR, University of Colorado.
\end{compactitem}

\section{Professional and Acedemic Associations}
CSDMS, Marine working group, Coastal working group, Cyberinfrastructure working group.

\bibliographystyle{../bst/agufull08-rev}
%\nocite{*}
\nocite{}

\end{document}


